The Dynamics of Anthropomorphism in Human-Robot Interaction

### 2014-04-04 paper.tex
started measuring anthropomorphism paragraph

Naturally, conflicts in how terms are used lead to a diversity of understandings
of the phenomenon which is described.  One reason for this might be that
anthropomorphism is a phenomenon that is studied in very different domains that
might each integrate their own understanding, use the same term to refer to
different things.  Despite the fact that there is no commonly accepted
definition, the terms \textit{anthropomorphism}, \textit{anthropomorphic} or
\textit{human-like} are often used as if their meanings were clear and agreed
upon \citep{persson_anthropomorphism_2000}. It is even argued that these terms
might be misused \citep{duffy_anthropomorphism_2002,epley_when_2008}.  For
instance, some researchers refer to \textit{``the robot's level of
anthropomorphism''} \citep{bartneck_is_2007}, whereas others disagree to such a
statement because they understand that a system or artifact itself does not
\textit{``contain anthropomorphism''} but only gives rise to the process of
anthropomorphizing in a given user and situation. Consequently,
\cite{persson_anthropomorphism_2000} conclude that anthropomorphism emerges in
the \textit{interaction} between the technology and the user, and has to be
understood as such. We come back on this point in the next section.

@@

However, we should \textit{not} use the term \emph{anthropomorphism} to refer to
the design of a non-human agent or artifact. To refer to an imitation of
human-like form in the \textit{design} of artificial agents, we use the term
\textbf{anthropomorphic design}. This explicit terminology prevents the commonly
encountered confusion between anthropomorphism as a psychological, subjective
phenomenon, and the external, objective factors that \emph{influence} the
phenomenon itself.

@@

\fxwarning{To be completed/rephrased into a discussion}

\citep{ruijten_introducing_2014}

>>>>

Naturally, conflicts in how terms are used lead to a diversity of understandings
of the phenomenon which is described.  One reason for this might be that
anthropomorphism is a phenomenon that is studied in very different domains that
might each integrate their own understanding, use the same term to refer to
different things.  Despite the fact that there is no commonly accepted
definition, the terms \textit{anthropomorphism}, \textit{anthropomorphic} or
\textit{human-like} are often used as if their meanings were clear and agreed
upon \citep{persson_anthropomorphism_2000}. It is even argued that these terms
might be misused \citep{duffy_anthropomorphism_2002,epley_when_2008}.  For
instance, some researchers refer to \textit{``the robot's level of
anthropomorphism''} \citep{bartneck_is_2007,feil-seifer_human-robot_2008}, whereas others disagree to such a
statement because they understand that a system or artifact itself does not
\textit{``contain anthropomorphism''} but only gives rise to the process of
anthropomorphizing in a given user and situation. Consequently,
\cite{persson_anthropomorphism_2000} conclude that anthropomorphism emerges in
the \textit{interaction} between the technology and the user, and has to be
understood as such. We come back on this point in the next section.

@@

However, despite the fact that ``anthropomorphism'' literally means ``human form'' we propose that the term should \textit{not} be used to refer to
the \textit{form / design} of a non-human agent or artifact. To refer to an imitation of
human-like \textit{form / design} of artificial agents, we propose to use the term
\textbf{anthropomorphic design}. This explicit terminology prevents the commonly
encountered confusion between anthropomorphism as a psychological, subjective
phenomenon, and the external, objective factors that \emph{influence} the
phenomenon itself.

@@

%\fxwarning{To be completed/rephrased into a discussion}

With this extended understanding of anthropomorphism being determined by multiple factors and showing dynamics over time, it also becomes questionable if the metrics and techniques that are currently used to measure anthropomorphism are sufficient.
